Digital Twins for Ocean Robots

### 2024-11-29 paper/paper.tex
cosmetic improvements (2/2)

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_OceanOPS.png}}
\caption{Locations of ocean robots collecting data and planned deployments, on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
\label{fig:ocean-ops}
\end{figure}

>>>>

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20241129_OceanOPS.png}}
\caption{Ocean robots that were collecting data on {\it 2024/11/29} for three types of observations (blue, green, and red dots). Planned deployments of Argo profilers are also shown (purple dots). Data is from https://www.ocean-ops.org and queried via \pkg{OceanRobots.jl}.}
\label{fig:ocean-ops}
\end{figure}
